Using Kuiper Observations to Explore the Temporal Evolution of the Tidal Disruption Event AT2024wsd

### 2024-12-16 ASTR518/project/paper/main.tex
add files for submission

% imported packages
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{natbib}

@@

\section{Introduction}
One of the most energetic events in the universe occurs when an unfortunate star approaches within the tidal radius of a supermassive black hole (SMBH). This is called a tidal disruption event (TDE) and was first theorized by \citet{hills1975}. \citet{rees1988} later predicted that the star would be tidally disrupted with $\sim$half of the material circularizing into an accretion disk around the SMBH and the other $\sim$half being ejected from the system as unbound debris. The material in the accretion disk should then produce bright, transient X-ray emission as it is accreted onto the SMBH, similar to the picture of an Active Galactic Nuclei.

About a decade later, the first TDE candidates were discovered observationally as bright X-ray transients \citep{donley2002}. But, with the advent of large optical all sky surveys, TDEs were also discovered to emit at optical wavelengths \citep{iPTF,ZTF,panstarrstde}. The origin of this optical emission from TDEs remains an open question. The leading model is inverse compton scattering, typically called ``reprocessing'', of the high energy X-rays by gas in a torus surrounding the SMBH. Another possible model is that we are observing optical emission from the ejected material after it escapes the system and cools. \citet{gezari2021} provides a more detailed summary of these and additional models.

This boom in the discovery of optically bright TDEs in the past $\sim$decade has resulted in $\sim200$ known TDEs to date, with a current discovery rate of $\sim10/yr$. The properties of the TDE emission provides a unique insight into the sub-parsec circumnuclei environment of galaxies and insights into the details of SMBH accretion \citep{holoien2020,Newsome2024}. In the optical, many of these properties are extracted using a combination of lightcurve and spectral energy distribution fitting \citep{Mockler2019}. Even more, recent population analyses of the lightcurves and spectral evolution of these TDEs show potential correlations between the optical TDE emission and physical properties of the system (e.g. \citet{vanVelzen2021}). However, more data is needed to verify these potential correlations and distinguish between the potential optical emission models.

Since these correlations are based on $\lesssim 100$ TDEs, they require further exploration with larger datasets to verify. As a result, following up TDEs both photometrically and spectroscopically is essential to further our understanding of the relation between TDE emission and the host galaxy and SMBH properties. The commonly used modeling softwares, like \citet{Mockler2019}, rely heavily on a well constrained peak in the lightcurve of the TDE. This means that observing TDEs with numerous telescopes near peak brightness is essential for future analyses. Current all sky surveys, like the Zwicky Transient Facility \citep[ZTF]{ZTF}, provide well time sampled photometry with a few day cadence. But, other telescopes can help by observing the TDEs near peak and obtaining even better temporal sampling.

@@

\begin{table}
\caption{Observations Summary}
\label{tab:obs}
\begin{tabular}{lllrr}
\hline
Image Type & Filter & Start Time (UTC) & Exposure Time (s) & Number of Exposures \\
\hline
Target & Harris-B & 08:53:55.552 & 50.00 & 3 \\
Target & Harris-V & 09:08:13.975 & 50.00 & 3 \\
Target & Harris-R & 09:03:23.041 & 50.00 & 3 \\
Target & Bessell-U & 08:58:18.912 & 50.00 & 3 \\
Flat & Harris-B & 07:53:26.592 & 5.00 & 15 \\
Flat & Harris-R & 07:46:32.588 & 5.00 & 30 \\
Flat & Harris-V & 07:57:11.190 & 5.00 & 15 \\
Flat & Bessell-U & 08:09:02.293 & 30.00 & 15 \\
Bias & --- & 07:13:58.343 & 0.00 & 31 \\
Dark & --- & 07:08:36.314 & 30.00 & 5 \\
Dark & --- & 09:26:19.184 & 5.00 & 5 \\
Dark & --- & 09:19:58.097 & 50.00 & 5 \\
\hline
\end{tabular}
\end{table}

We observed the TDE AT2024wsd with the Kuiper 61'' telescope on Mt. Graham on the night of October 18-19, 2024 (Local Date). A summary of the Target and Calibration observations is given in Table \ref{tab:obs}. We observed the target with the Mont4k CCD in the Harris- R, B, V and Bessell- U filters. These filters are near identical to the standard Johnson/Cousin filter set. The flat images were taken with the dome flat capability of the Kuiper 61'' telescope. The bias and dark images were taken using standard methods. While this telescope is not typically used for transient followup observations, our observing time for class provided a unique opportunity to test it's capabilities.

\subsection{Data Calibration}
We performed standard bias calibration by stacking the bias images using an average with sigma clipping. The sigma clipping uses a $\pm 5 \sigma$ threshold to smooth the images over extreme outliers (e.g. hot pixels, cosmic rays, etc.). In future calibration steps, we use the same stacking parameters as used for the bias images. From the bias images, we estimate the read noise by subtracting off a random bias image from the master bias image ten times to create ten bias difference images. Since the bias images include both read noise and persistent detector signal, this renormalizes the bias images and removes extraneous outliers, leaving behind just the extra current due to read noise. Finally, we take the standard deviation of all of these images to find the read noise and convert from ADU to electrons using the gain  $G=3.1~e/ADU$ of Mont4k\footnote{https://james.as.arizona.edu/~psmith/61inch/CCD/basicinfo.html}.

@@

Finally, we apply all of these calibrations to the target images. First, we bias correct the target images using the master bias. Then, we subtract the 50s master dark image from the target images. We apply the flat correction to each bias and dark corrected target image for the corresponding filter. Then, we stack all of the corrected target images by filter to give 4 science images. We then use \texttt{astrometry.net} to compute the WCS solutions for each image. From these reduced images, we remove the chip gap by using a scanning method with a tophat kernel that averages over the 4 pixels on either side of the gap. This leaves us with the images in Figure \ref{fig:targ}.

@@

Once we have a background subtracted signal, we need to convert from photon counts to physical units. To do this, we query the VizieR data service for Johnson/Cousins magnitudes in our field of view. We follow the same procedure as used for the target for each of these stars in the field of view: 1) place ana 5'' aperture  over each source and find the sum of the counts; 2) Find and subtract the background using an annulus with a 5'' inner radius and 10'' outer radius; and 3) Convert from ADU to electrons and photons. The aperture placed on each of these foreground stars is shown as a blue circle in Figure \ref{fig:targ}. Each of these foreground stars has synthetic Johnson/Cousins magnitudes generated from the Gaia BP and RP mean spectra of the sources \citep{gaiadr3,gaiadr3_syntphot} (VizieR catalog I/360/syntphot). Note that we choose to use the Johnson/Cousins filter system since it is very similar to the Harris and Bessell filters but a more common standard. This, of course, introduces a level of systematic uncertainty into our magnitude calculation but this is negligible compared to the  uncertainties on our flux calculations. From these synthetic magnitudes, we find the zero point, $f_0$ of each filter using equation \ref{eq:f0},

@@

We take the median of the computed zero points from each of these foreground stars to find a single zero point for the Mont4k detector. We choose to use the median to make our zero point calculation robust to outliers like variable stars or possible contaminating galaxies. The calculated zero points in photon counts are listed in Table \ref{tab:res}. Using the computed zero points we calculate the magnitude for each filter of our source using the standard flux-magnitude equation,

@@

\subsection{Lightcurve Modeling}
To compare the magnitudes measured at Kuiper to other public photometry we pull all of the available photometry on the Transient Name Server page for AT2024wsd\footnote{https://www.wis-tns.org/object/2024wsd} which consists mostly of Zwicky Transient Facility (ZTF) preliminary detections. The Kuiper photometry and public photometry are shown for comparison in Figure \ref{fig:lc}. We also query the Asteroid Terrestrial-impact Last Alert System (ATLAS) forced photometry service for archival photometry of this target. The ATLAS query revealed all nondetections, which are also shown in Figure \ref{fig:lc}. To compare the public photometry to our Kuiper data, we assume that the measurements in the Johnson/Cousins filters are similar to those made in the ZTF b, g, and r filters because the effective wavelengths tend to be within a few hundred angstroms. There are obviously limitations to this assumption but it is our only option given the lack of {\it public} photometry for this object. There is no public photometry available for the Bessell-U filter so we are unable to derive rise rates for this filter.

@@

\begin{table}
  \centering
  \caption{Reduction Results}
  \label{tab:res}
  \begin{tabular}{lllll}
    \hline
    Filter & Harris-B & Harris-V & Harris-R & Bessell-U \\
    \hline
    Source Aperture Sum (ADU) & 351531.39 & 524268.83 & 554351.81 & 94429.37 \\
    Source Aperture Sum (e) & 1089747.30 & 1625233.38 & 1718490.61 & 292731.06 \\
    Source Aperture Sum ($\gamma$) & 1814854.11 & 2706647.21 & 2861956.85 & 487511.34 \\
    \hline
    Background Annulus Sum (ADU) & 348945.20 & 522267.83 & 549786.75 & 93693.18 \\
    Background Annulus Sum (e) & 1081730.11 & 1619030.28 & 1704338.91 & 290448.86 \\
    Background Annulus Sum ($\gamma$) & 1801502.37 & 2696316.62 & 2838388.76 & 483710.59 \\
    \hline
    Dark Noise ($\sigma_D$; ADU/pixel) & 0.29 & 0.29 & 0.29 & 0.29 \\
    Dark Noise ($\sigma_D$; e/pixel) & 0.51 & 0.51 & 0.51 & 0.51 \\
    \hline
    Read Noise ($\sigma_R$; ADU/pixel) & 3.04 & 3.04 & 3.04 & 3.04 \\
    Read Noise ($\sigma_R$; e/pixel) & 9.41 & 9.41 & 9.41 & 9.41 \\
    \hline
    Signal ($f_e$; e) & 8017.18 & 6203.11 & 14151.70 & 2282.20 \\
    Signal ($f_\gamma$; $\gamma$) & 13351.74 & 10330.59 & 23568.10 & 3800.75 \\
    Zero Point ($10^{12}f_0$; $\gamma$) & 0.31 & 0.46 & 0.44 & 0.05 \\
    Apparent Magnitude & 18.41 & 19.12 & 18.18 & 17.74 \\
    Apparent Magnitude Error & 0.12 & 0.19 & 0.09 & 0.23 \\
    \hline
    SNR & 7.55 & 4.81 & 10.68 & 3.96 \\
    \hline
  \end{tabular}
\end{table}

A summary of our data reduction and zero point calibration results is in table \ref{tab:res}. From these calibrations, we compute a signal-to-noise ratio, derived both theoretically (\S\ref{sec:snr_theory}) and observationally (\S\ref{sec:snr_obs}), in the subsequent sections.

@@

\subsection{Zero Point Calibration and Lightcurve Fit Results}
\begin{figure}
  \includegraphics[width=\textwidth]{../analysis/lightcurve.png}
  \label{fig:lc}
  \caption{Light curve, or magnitude as a function of days since discovery, of both the publicly available photometry (circles) and photometry (squares) from this work. ATLAS upperlimits are shown as downward facing triangles in both their cyan filter and orange filter. The best fit linear rise models are shown as dashed lines where the color corresponds to the color of the data points it is a fit for.}
\end{figure}

@@

Another important lesson from this is that the Kuiper telescope is not optimized for photometric follow up of transient events. This is because we would need nearly nightly, or at least weekly, time on the telescope to improve our temporal sampling of the lightcurve. Or, using some Kuiper observations in combination with the more complete, but private, ATLAS and ZTF datasets. In the end, because ZTF and ATLAS follow up these transients on a nightly basis, it would probbaly make more sense to let them get the photometry and we use Kuiper for spectrographic followup and classification of transients in the future.

Finally, It is important to note that in the literature the rise rate and rise time of tidal disruption events is typically found with a gaussian fit to the data \citep{gezari2021, vanVelzen2021}. However, with our limited dataset, such a fit would be nearly impossible to perform. In the future, it would, once again, be beneficial to include a better temporally sampled dataset to better constrain the peak, and therefore rise time, of the lightcurve.

@@

The results of these observations are explained in detail in \S\ref{sec:res}. Our signal to noise ratio ranges from $\sim4$ to $\sim10$ depending on the filter used. The magnitudes we found are about 1 mag brighter than previous public photometry. This was expected since the rise time of TDE optical emission tends to be around a month and we were observing AT2024wsd about 3 weeks after initial discovery. Using a combination of our photometry and previous public photometry, we find a gradual rise to the approximate peak brightness around $20$ days after discovery of about $-0.05$ mag/day, depending on the filter used. This rise rate was derived using a linear fit to our limited dataset and is poorly constrained. This rise time reported here should be treated as a lower limit since we have no photometry during the lightcurve decay.

@@

>>>>

% imported packages
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{longtable}

% some journal abbreviations for the bib file
\newcommand\AJ{AJ}%        % Astronomical Journal

@@

\section{Introduction}
One of the most energetic events in the universe occurs when an unfortunate star approaches within the tidal radius of a supermassive black hole (SMBH). This is called a tidal disruption event (TDE) and was first theorized by \citet{hills1975}. \citet{rees1988} later predicted that the star would be tidally disrupted with $\sim$half of the material circularizing into an accretion disk around the SMBH and the other $\sim$half being ejected from the system as unbound debris. The material in the accretion disk should then produce bright, transient X-ray emission as it is accreted onto the SMBH.

About a decade later, the first TDE candidates were discovered observationally as bright X-ray transients \citep{donley2002}. More recently, with the advent of large optical all sky surveys, TDEs were also discovered to emit at optical wavelengths \citep{iPTF,ZTF,panstarrstde}. The origin of this optical emission from TDEs remains an open question (2020 Decadel Survey, Subsection B-Q2a). The leading model is inverse compton scattering, typically called ``reprocessing'', of the high energy X-rays by gas in a torus surrounding the SMBH. Another possible model is that we are observing optical emission from the ejected material after it escapes the system and cools. \citet{gezari2021} provides a more detailed summary of these and additional models.

This boom in the discovery of optically bright TDEs in the past $\sim$decade has resulted in $\sim200$ known TDEs to date, with a current discovery rate of $\sim10/yr$. The properties of the TDE emission provides a unique insight into the sub-parsec circumnuclei environment of galaxies and insights into the details of SMBH accretion \citep{holoien2020,Newsome2024}. In the optical, many of these properties are extracted using a combination of light-curve and spectral energy distribution fitting \citep{Mockler2019}. Even more, recent population analyses of the light-curves and spectral evolution of these TDEs show potential correlations between the optical TDE emission and physical properties of the system (e.g. \citet{vanVelzen2021}). However, more data is needed to verify these potential correlations and distinguish between the potential optical emission models.

Since these correlations are based on $\lesssim 100$ TDEs, they require further exploration with larger datasets to verify. As a result, following up TDEs both photometrically and spectroscopically is essential to further our understanding of the relation between TDE emission and the host galaxy and SMBH properties. The commonly used modeling softwares, like \citet{Mockler2019}, rely heavily on a well constrained peak in the light-curve of the TDE. This means that observing TDEs with numerous telescopes near peak brightness is essential for future analyses. Current all sky surveys, like the Zwicky Transient Facility \citep[ZTF]{ZTF}, provide well time sampled photometry with a few day cadence. But, other telescopes can help by observing the TDEs near peak and obtaining even better temporal sampling.

@@

\begin{table}
  \centering
  \caption{Observations Summary}
  \label{tab:obs}
  \begin{tabular}{lllrr}
    \hline
    Image Type & Filter & Start Time (UTC) & Exposure Time (s) & Number of Exposures \\
    \hline
    Target & Harris-B & 08:53:55.552 & 50.00 & 3 \\
    Target & Harris-V & 09:08:13.975 & 50.00 & 3 \\
    Target & Harris-R & 09:03:23.041 & 50.00 & 3 \\
    Target & Bessell-U & 08:58:18.912 & 50.00 & 3 \\
    Flat & Harris-B & 07:53:26.592 & 5.00 & 15 \\
    Flat & Harris-R & 07:46:32.588 & 5.00 & 30 \\
    Flat & Harris-V & 07:57:11.190 & 5.00 & 15 \\
    Flat & Bessell-U & 08:09:02.293 & 30.00 & 15 \\
    Bias & --- & 07:13:58.343 & 0.00 & 31 \\
    Dark & --- & 07:08:36.314 & 30.00 & 5 \\
    Dark & --- & 09:26:19.184 & 5.00 & 5 \\
    Dark & --- & 09:19:58.097 & 50.00 & 5 \\
    \hline
  \end{tabular}
\end{table}

We observed the TDE AT2024wsd with the Kuiper 61'' telescope on Mt. Graham on the night of October 18-19, 2024 (Local Date). A summary of the Target and Calibration observations is given in Table \ref{tab:obs}. We observed the target with the Mont4k CCD in the Harris- R, B, V and Bessell- U filters. The flat images were taken with the dome flat capability of the Kuiper 61'' telescope. The bias and dark images were taken using standard methods. While this telescope is not typically used for transient followup observations, our observing time for class provided a unique opportunity to test it's capabilities.

\subsection{Data Calibration}
We performed standard bias calibration by stacking the bias images using an average with sigma clipping. The sigma clipping uses a $\pm 5 \sigma$ threshold to smooth the images over extreme outliers (e.g. hot pixels, cosmic rays, etc.). In future calibration steps, we use the same stacking parameters as used for the bias images. From the bias images, we estimate the read noise by subtracting off a random bias image from the master bias image ten times to create ten bias difference images. Since the bias images include both read noise and persistent detector signal, this renormalizes the bias images and removes extraneous outliers, leaving behind just the extra current due to read noise. Finally, we take the standard deviation of all of these images to find the read noise and convert from ADU to electrons using the gain  $G=3.1~e/ADU$ of Mont4k\footnote{\url{https://james.as.arizona.edu/~psmith/61inch/CCD/basicinfo.html}}.

@@

Finally, we apply all of these calibrations to the target images. First, we bias correct the target images using the master bias. Then, we subtract the 50s master dark image from the target images. We apply the flat correction to each bias and dark corrected target image for the corresponding filter. Then, we stack all of the corrected target images by filter to give 4 science images. We then use \texttt{astrometry.net} \citep{lang2010} to compute the WCS solutions for each image. From these reduced images, we remove the chip gap by using a scanning method with a tophat kernel that averages over the 4 pixels on either side of the gap. This leaves us with the images in Figure \ref{fig:targ}.

@@

Once we have a background subtracted signal, we need to convert from photon counts to physical units. To do this, we query the VizieR data service for Johnson/Cousins magnitudes in our field of view. We follow the same procedure as used for the target for each of these stars in the field of view: 1) place a 5'' aperture  over each source and find the sum of the counts; 2) Find and subtract the background using an annulus with a 5'' inner radius and 10'' outer radius; and 3) Convert from ADU to electrons and photons. The aperture placed on each of these foreground stars is shown as a blue circle in Figure \ref{fig:targ}. We did this for 19 foreground stars and the results of the aperture photometry and background annulus estimation for one source are given in Table \ref{tab:res}.

Each of these foreground stars has synthetic Johnson/Cousins magnitudes generated from the Gaia BP and RP mean spectra of the sources \citep{gaiadr3,gaiadr3_syntphot} (VizieR catalog I/360/syntphot). Note that we choose to use the Johnson/Cousins filter system since it is very similar to the Harris and Bessell filters but a more common standard. This, of course, introduces a level of systematic uncertainty into our magnitude calculation but this is negligible compared to the  uncertainties on our flux calculations. From these synthetic magnitudes, we find the zero point, $f_0$ of each filter using equation \ref{eq:f0},

@@

\noindent We take the median of the computed zero points from each of these foreground stars to find a single zero point for the Mont4k detector. We choose to use the median to make our zero point calculation robust to outliers like variable stars or possible contaminating galaxies. The calculated zero points in photon counts are listed in Table \ref{tab:res}. Using the computed zero points we calculate the magnitude for each filter of our source using the standard flux-magnitude equation,

@@

\subsection{Light-Curve Modeling}
To compare the magnitudes measured at Kuiper to other public photometry we pull all of the available photometry on the Transient Name Server page for AT2024wsd\footnote{https://www.wis-tns.org/object/2024wsd} which consists mostly of Zwicky Transient Facility (ZTF) preliminary detections. The Kuiper photometry and public photometry are shown for comparison in Figure \ref{fig:lc}. We also query the Asteroid Terrestrial-impact Last Alert System (ATLAS) forced photometry service for archival photometry of this target. The ATLAS query revealed all nondetections, which are also shown in Figure \ref{fig:lc}. To compare the public photometry to our Kuiper data, we assume that the measurements in the Johnson/Cousins filters are similar to those made in the ZTF b, g, and r filters because the effective wavelengths tend to be within a few hundred angstroms. There are obviously limitations to this assumption but it is our only option given the lack of {\it public} photometry for this object. There is no public photometry available for the Bessell-U filter so we are unable to derive rise rates for this filter.

@@

\begin{table}
  \centering
  \caption{Reduction Results}
  \label{tab:res}
  \begin{longtable}{lllll}
    \hline
    Filter & Harris-R & Harris-B & Harris-V & Bessell-U \\
    \hline
    Source Aperture Sum (ADU) & 554351.81 & 351531.39 & 524268.83 & 94429.37 \\
    Source Aperture Sum (e) & 1718490.61 & 1089747.30 & 1625233.38 & 292731.06 \\
    Source Aperture Sum ($\gamma$) & 2861956.85 & 1814854.11 & 2706647.21 & 487511.34 \\
    \hline
    Background Annulus Sum (ADU) & 548693.02 & 348232.62 & 521197.05 & 93495.58 \\
    Background Annulus Sum (e) & 1700948.36 & 1079521.11 & 1615710.86 & 289836.31 \\
    Background Annulus Sum ($\gamma$) & 2832742.16 & 1797823.52 & 2690788.50 & 482690.45 \\
    \hline
    Dark Noise ($\sigma_D$; ADU/pixel) & 0.29 & 0.29 & 0.29 & 0.29 \\
    Dark Noise ($\sigma_D$; e/pixel) & 0.51 & 0.51 & 0.51 & 0.51 \\
    \hline
    Read Noise ($\sigma_R$; ADU/pixel) & 3.15 & 3.15 & 3.15 & 3.15 \\
    Read Noise ($\sigma_R$; e/pixel) & 9.76 & 9.76 & 9.76 & 9.76 \\
    \hline
    Target Signal ($f_e$; e) & 17542.25 & 10226.19 & 9522.52 & 2894.75 \\
    Target Signal ($f_\gamma$; $\gamma$) & 29214.69 & 17030.59 & 15858.71 & 4820.89 \\
    Noise on Target (e) & 1326.70 & 1063.67 & 1291.08 & 578.25 \\
    SNR for Target & 13.22 & 9.61 & 7.38 & 5.01 \\
    \hline
    Sample Flux Cal. Aperture Sum (ADU)\footnote{This from 1 of the 19 foreground stars used to estimate the zero point. The others are available upon request.} & 786324.66 & 413693.58 & 692494.86 & 102921.67 \\
    Sample Flux Cal. Background Annulus Sum (ADU) & 583842.18 & 356051.85 & 543212.76 & 94262.53 \\
    Sample Flux Cal. Signal (ADU) & 202482.48 & 57641.73 & 149282.10 & 8659.14 \\
    Sample Flux Cal. Signal (e) & 627695.68 & 178689.35 & 462774.51 & 26843.33 \\
    Sample Flux Cal. Signal ($\gamma$) & 1045358.02 & 297587.43 & 770699.97 & 44704.61 \\
    Sample Flux Cal. Noise (e) & 1574.56 & 1150.69 & 1479.32 & 600.58 \\
    \hline
    Zero Point ($10^{12}f_0$; $\gamma$) & 0.44 & 0.32 & 0.47 & 0.05 \\
    Apparent Magnitude & 17.95 & 18.18 & 18.67 & 17.51 \\
    Apparent Magnitude Error & 0.07 & 0.10 & 0.12 & 0.18 \\
    \hline
  \end{longtable}
  \centering
  \vspace{-0.75cm}
\end{table}
A summary of our data reduction and zero point calibration results is in table \ref{tab:res}. From these calibrations, we compute a signal-to-noise ratio, derived both theoretically (\S\ref{sec:snr_theory}) and observationally (\S\ref{sec:snr_obs}), in the subsequent sections.

@@

\subsection{Zero Point Calibration and Light-Curve Fit Results}
\begin{figure}
  \includegraphics[width=\textwidth]{../analysis/lightcurve.png}
  \label{fig:lc}
  \caption{Light curve, or magnitude as a function of days since discovery, of both the publicly available photometry (circles) and photometry (squares) from this work. ATLAS upperlimits are shown as downward facing triangles in both their cyan filter and orange filter. The best fit linear rise models are shown as dashed lines where the color corresponds to the color of the data points it is a fit for.}
\end{figure}

@@

Another important lesson from this is that the Kuiper telescope is not optimized for photometric follow up of transient events. This is because we would need nearly nightly, or at least weekly, time on the telescope to improve our temporal sampling of the light-curve. Or, using some Kuiper observations in combination with the more complete, but private, ATLAS and ZTF datasets. In the end, because ZTF and ATLAS follow up these transients on a nightly basis, it would probably make more sense to let them get the photometry and we use Kuiper for spectrographic followup and classification of transients in the future.

Finally, It is important to note that in the literature the rise rate and rise time of tidal disruption events is typically found with a gaussian fit to the data \citep{gezari2021, vanVelzen2021}. However, with our limited dataset, such a fit would be nearly impossible to perform. In the future, it would, once again, be beneficial to include a better temporally sampled dataset to better constrain the peak, and therefore rise time, of the light-curve.

@@

The results of these observations are explained in detail in \S\ref{sec:res} and given in Table \ref{tab:res}. Our signal to noise ratio ranges from $\sim4$ to $\sim10$ depending on the filter used. The magnitudes we found are about 1 mag brighter than previous public photometry. This was expected since the rise time of TDE optical emission tends to be around a month and we were observing AT2024wsd about 3 weeks after initial discovery. Using a combination of our photometry and previous public photometry, we find a gradual rise to the approximate peak brightness around $20$ days after discovery of about $-0.05$ mag/day, depending on the filter used. This rise rate was derived using a linear fit to our limited dataset and is poorly constrained. This rise time reported here should be treated as a lower limit since we have no photometry during the light-curve decay.

@@

\software{
  \citet{lang2010},
  \citet{photutils},
  \citet{ccdproc},
  \citet{astropy:2022},
  \citet{numpy},
  \citet{pandas-ds},
  \citet{pandas-zenodo}
}
